pyTopoComplexity: A Python package for topographic complexity analysis

### 2024-08-19 JOSS/paper.rmd
Add files via upload

---
title: 'pyTopoComplexity: A Python package for topographic complexity analysis'
tags:
  - Python
  - topographic complexity
  - surface roughness
  - two-dimensional continuous wavelet transform
  - fractal dimension
  - rugosity index
authors:
  - name: Larry Syu-Heng Lai
    corresponding: true
    orcid: 0000-0003-4589-9729 
    affiliation: "1"
  - name: Adam M. Booth
    orcid: 0000-0002-7339-0594   
    affiliation: "2"
  - name: Alison R. Duvall
    orcid: 0000-0002-7760-7236 
    affiliation: "1"
  - name: Erich Herzig
    orcid: 0000-0002-3898-5971 
    affiliation: "1"
affiliations:
 - name: Department of Earth and Space Sciences, University of Washington, Seattle, Washington, USA
   index: 1
 - name: Department of Geology, Portland State University, Portland, Oregon, USA
   index: 2
date: 31 August 2024
bibliography: paper.bib
---

>>>>

---
title: 'pyTopoComplexity: A Python package for topographic complexity analysis'
tags:
  - Python
  - topographic complexity
  - surface roughness
  - two-dimensional continuous wavelet transform
  - fractal dimension
  - rugosity index
authors:
  - name: Larry Syu-Heng Lai
    corresponding: true
    orcid: 0000-0003-4589-9729 
    affiliation: "1"
  - name: Adam M. Booth
    orcid: 0000-0002-7339-0594   
    affiliation: "2"
  - name: Alison R. Duvall
    orcid: 0000-0002-7760-7236 
    affiliation: "1"
  - name: Erich Herzig
    orcid: 0000-0002-3898-5971 
    affiliation: "1"
affiliations:
 - name: Department of Earth and Space Sciences, University of Washington, Seattle, Washington, USA
   index: 1
 - name: Department of Geology, Portland State University, Portland, Oregon, USA
   index: 2
date: 18 August 2024
bibliography: paper.bib
---
